### 2017-03-22 grlp.tex
Relaxed program text

Now, let $\phi_1,\ldots,\phi_k : \S \to \R$ be $k$ basis functions. 
\todoc{I think we should use $d$ to denote the number of basis functions. Or at least $n$. Low priority.} 
The \emph{Approximate Linear Program} (ALP) of \citet{SchSei85} 
is obtained by adding the linear constraints $J = \sum_{i=1}^k r_i \phi_i$ to the above linear program. Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \R^k \}$.
As noted by \citet{SchSei85}, the linear program is feasible as long as $\one$, defined as the vector with all components being identically equal to one, is in the span of $\{\phi_1,\dots,\phi_k\}$. 
\emph{For the purpose of computations, it is assumed that the values $c^\top \phi_i$, $i=1,\dots, k$ and the values $(P_a \phi_i)(s)$ and $g_a(s)$ can be accessed in constant time.} 
This assumption can be relaxed to assuming that one can access $g_a(s)$ and $\phi_i(s)$ for any $(s,a)$ in constant time, as well as to that one can efficiently sample from $c$, from $P_a(s,\cdot)$ for any $(s,a)$ pair, 
but the details of this are the beyond the scope of the present work. As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm.

While evaluating the objective and checking a single constraint for constraint violations can be done in constant time, 
since the number of constraints in the ALP is equal to the number of state-action pairs, the ALP is still intractable in general.
To reduce the number of constraints, we propose to relax the constraints by considering a linear projection of them with 
positive linear coefficients. Since the resulting program may become unbounded, it is necessary to introduce an additional constraint $r\in \N$, where $\N$ will be chosen to be large enough so as not to exclude ``good solutions'', while constraining enough so as to prevent unbounded solutions. \todoc{I still don't get whether we need or not $\N$. Under the conic constraints, do we need it or not? I mean when $r$ hits the boundary of $\N$ I have the feeling that we get a very bad solution and it would not then matter much whether $\N$ is even there or not.}

>>>>

Now, let $\phi_1,\ldots,\phi_k : \S \to \R$ be $k$ basis functions. 
\todoc{I think we should use $d$ to denote the number of basis functions. Or at least $n$. Low priority.} 
The \emph{Approximate Linear Program} (ALP) of \citet{SchSei85} 
is obtained by adding the linear constraints $J = \sum_{i=1}^k r_i \phi_i$ to the above linear program. Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \R^k \}$.
As noted by \citet{SchSei85}, the linear program is feasible as long as $\one$, defined as the vector with all components being identically equal to one, is in the span of $\{\phi_1,\dots,\phi_k\}$. 
\emph{For the purpose of computations, it is assumed that the values $c^\top \phi_i$, $i=1,\dots, k$ and the values $(P_a \phi_i)(s)$ and $g_a(s)$ can be accessed in constant time.} 
This assumption can be relaxed to assuming that one can access $g_a(s)$ and $\phi_i(s)$ for any $(s,a)$ in constant time, as well as to that one can efficiently sample from $c$, from $P_a(s,\cdot)$ for any $(s,a)$ pair, 
but the details of this are the beyond the scope of the present work. As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi \ralp$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$, where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm and $\Phi \in \R^{S\times k}$ is the matrix formed by $(\phi_1,\dots,\phi_k)$. That the error of approximating $J^*$ with $\Jalp$ is $O(\epsilon)$ is significant: The user can focus on finding a good basis, leaving the search for the ``right'' coefficients to a linear program solver.

While the solving the ALP can be significantly cheaper than solving the LP underlying the MDP
and thus it can be advantageous for moderate-scale MDPs,
 \todoc{Give the big-Oh costs!} the number of constraints in the ALP is $SA$, 
 hence the ALP is still infeasible for huge-scale MDPs. 
%While evaluating the objective and checking a single constraint for constraint violations can be done in constant time, 
%since the number of constraints in the ALP is equal to the number of state-action pairs, 
%the ALP is still intractable in general.
To reduce the number of constraints, we consider a relaxation of ALP 
where the constraints are replaced with positive linear 
combinations of them. 
Recalling that the constraints took the form $J \ge g_a + \alpha P_a J$ (with $J = \Phi r$),
choosing $m$ to be target number of constraints, for $1\le i \le m$, the $i$th new constraint is given by
$\sum_a w_{i,a}^\top J \ge \sum_a w_{i,a}^\top(g_a + \alpha P_a J)$, 
where the choice of $m$ and that of the vectors $w_{i,a}\in [0,\infty)^S$ is left to the user.
Note that this results in a linear program with $k$ variables and $m$ constraints, which can be written as
\begin{align}\label{grlp}
\begin{split}
&\underset{r\in \R^k}{\min}\, \, c^\top \Phi r\\
&\text{s.t.}\mb  \,\sum_a W_a^\top \Phi r\geq \sum_a W_a^\top (g_a + \alpha P_a) \Phi r\,,
\end{split}
\end{align}
where $W_a = (w_{1,a},\dots,w_{m,a}) \in [0,\infty)^{S \times m}$. 
\todoc{Do we need that $(w_{i,a}^\top)_i$ defines a probability distribution?}
Note that the $(i,j)$th entry of the $m\times k$ constraint matrix of the resulting LP is
$\sum_a  w_{i,a}^\top  \phi_j - \alpha \sum_a w_{i,a}^\top P_a \phi_j$ and assuming that $(w_{i,a})_{a}$ has $p$ nonzero
elements, this can be calculated in $O( p )$ time, making the total cost of obtaining the constraint matrix to be $O(mkp)$ regardless the value of $S$ and $A$. \todoc{Somewhere discuss that the cost of obtaining a policy will depend on $A$. 
We can also discuss how $A$ could be folded into states.}

We will call the LP in \eqref{grlp} the \emph{linearly relaxed approximate linear program (LRALP)}. \todoc{Replace GRLP everywhere with LRALP.} Note that the LRALP may be unbounded. While unboundedness could be prevented by adding an extra constraint of the form $r\in \N$ for a ``sufficiently large'' and ``simple'' bounded polytope $\N \subset \R^k$ which can be chosen based on the knowledge of $\alpha$ alone. However, we see little value in this and thus stick to the above simple form.%
\footnote{
Note though that $\N$ would need to be chosen based on very little information,
hence it would in general be chosen to provide an extremely loose constraint to avoid
the accidental elimination of potentially good solutions. 
Hence, on the occasion when the LP without the extra $r\in \N$ constraint is unbounded,
the solution found when $r\in \N$ is added would lie on the boundary of $\N$, which
makes one expect the error of the resulting solution to be rather large.
}

Since the resulting program may become unbounded,  it is necessary to introduce an additional constraint $r\in \N$, where $\N$ will be chosen to be large enough so as not to exclude ``good solutions'', while constraining enough so as to prevent unbounded solutions. 
